SHARP IV: Flux ratio anomalies from disks in the Illustris simulation

### 2016-08-11 papers/illustris_disk/ms.tex
update illustris paper draft

\subsection{Kinematical selection I}
In kinematical view, stellar disk is a group of stars co-rotate in the same direction with the common symmetric axis. One of the advantages in simulations is that one can access to the full detail of kinematical properties for single mass particle. These kinematical properties provide an approach to decompose different components in disk galaxy: thin disk, thick disk, and spheroid.
z-component angular momentum (symmetric axis)
Jz vs binding energy: $J_{circ}$ curve
circularity parameter $\epsilon_z = Jz/J_{circ}$

decomposition: thin disk+thick disk+spheroid

thin disk star fraction larger than 40\%

\subsection{Kinematical selection II}
stars in spheroid: bulge stars
bulge star fraction less than 60\%
\section{Disk properties}
\begin{itemize}
\item how many galaxies have disks
\item mass in disk
\item redshift evolution
\item comparison with B1555 and SWELLS
\item observability of the disks
\end{itemize}
\section{Flux ratio anomalies from disks}

>>>>

\subsection{Kinematical selection I}
In kinematical view, stellar disk is a group of stars co-rotate in the same direction around the  symmetric axis (we will call this symmetric axis ``z-axis,'' for short.) One of the advantages in simulations is that one can access to the full detail of kinematical properties for single mass particle. These kinematical properties provide an approach to decompose different components in disk galaxy: thin disk, thick disk, and spheroid. The dynamical decomposition can be done in the parameter space of the z-component of specific angular momemtum, $J_z$, and the specific binding energy, $E$, of each star (Abadi, et al. 2003). On the $J_z - E$ plane, stellar and gaseous components co-rorating in the same direction define a solid curve $J_{circ}(E)$ (see Fig.2 in Abadi, et al. 2003), which represents the coratating circular orbits in the disk as a function of specific binding energy. The circularity parameter $\epsilon_z$ of each star is defined as the ratio between its  $J_z$ and corresponding $J_{circ}(E)$, showing how closely a stellar or gaseous component follows the circular motion of the disk. In general, the gaseous disk and the thin disk stellar components have a sharp distribution of $\epsilon_z$ peaked about unity. Base on the $\epsilon_z$ distribution, all stars within the ``luminous'' radius can be decomposed into three different dynamical components: a spheriod (including bulge and halo stars), thin disk (stars with $\epsilon_z > 0.7$), and thick disk. Galaxies with more than 40 per cent of stars in thin disk are considered as late-type spirals.

\subsection{Kinematical selection II}
Having more than 40 per cent of stars in thin disk is a strict criteria which selects the galaxies with a large disk and a small bulge. However, spirals with a smaller thin disk but large enough thick disk may also provide sufficient gravitational perturbation to influence lens image flux ratios. Thus we select galaxies having more than 40 per cent stars in their thin disk and thick disk, in another word, galaxies having less than 60 per cent of stars in bulge and halo as the second kinematical selection of disk galaxies.

\section{Disk properties}
\begin{itemize}
\item how many galaxies have disks
\item mass in disk
\item redshift evolution
\item comparison with B1555 and SWELLS
\item observability of the disks
\end{itemize}
\section{Flux ratio anomalies from disks}
